---
title: "Specific Aim 1 Obesity Certification Analysis"
author: "Last Updated by: Catherine Pollack"
date: "Last Updated: November 4, 2020"
output: html_notebook
---

# Install libraries and packages
```{r}
library(tidyverse) #For everything
library(datasets) #For state abbreviations
library(splitstackshape) #For splitting columns
library(readxl) #For reading in excel files
library(data.table) #Partial string matching
library(hash) #For table of hospitals
library(reshape2) #For creating the list of hospitals 
library(stringdist) #For calculating string similarity
library(purrr) #For extracting list elements from a large list
library(openintro) #For converting state abbreviations to names 
library(tidygeocoder) #For converting addresses to lat-long
library(magrittr) #%<>%
```

# Bring in data sets
```{r}
setwd("~/Documents/Dartmouth/Research/Obesity Certification/Data")
additional <- read.csv('ABOM_Additional191011.csv', stringsAsFactors = FALSE)
additional_DO <- read.csv('ABOM_Additional_DO191015.csv', stringsAsFactors = FALSE)
additional_US <- read.csv('ABOM_DoxViaUSNews_191015.csv', stringsAsFactors = FALSE)
originally_missed <- read.csv('200504_MissingData.csv', stringsAsFactors = FALSE)
```

# Read in National Data File
```{r}
setwd("~/Documents/Dartmouth/Research/Obesity Certification/Data") #Set Working Directory
counties <- read.delim("NationalFile_20190901 2.txt", sep = "|")
```

# Keep only places or hospitals
```{r}
counties %<>%
  filter(FEATURE_CLASS == "Populated Place" | FEATURE_CLASS == "Hospital") %>%
  select(FEATURE_NAME, FEATURE_CLASS, STATE_ALPHA, COUNTY_NAME, PRIM_LAT_DEC, PRIM_LONG_DEC)
```

# Separate out hospital names
```{r}
hospitals <- filter(counties, FEATURE_CLASS == "Hospital")
```

# Remove <td> and </td>
```{r}
abom <- data.frame(lapply(abom, function(x) {gsub("<td>", "", x)}))
abom <- data.frame(lapply(abom, function(x) {gsub("</td>", "", x)}))
```

# Replace ASCII string with "&"
```{r}
abom$Additional.Board.Certification <- abom$Additional.Board.Certification %>%
  str_replace_all("&amp;", "&")
```

# Split off list of names
```{r}
names <- abom$Name
```

# Check if there are any overlapping names
```{r}
names <- as.character(names) #Splits off names

length(unique(names)) == length(names) #Checks if there are overlapping names
```

# Pull the names that appear more than once
```{r}
names_duplicates <- names[which(duplicated(names) == TRUE)] #Pull the names that are duplicated
names_nodups <- names[!names %in% names_duplicates]
```

# Export name CSVs -- MAKE SURE TO CHANGE FILE NAME BEFORE RUNNING
```{r}
#write.csv(names_nodups, file = "NoDuplicatedNames_191011.csv")
#write.csv(names_duplicates, file = "DuplicatedNames_191011.csv")
```

# Separate out names that weren't pulled in Doximity initial search
```{r}
names_leftout <- filter(additional, address.info == "")
names_leftout <- inner_join(names_leftout, abom, by = "Name") %>%
  select(Name, City, State.Province) %>%
  filter(State.Province %in% datasets::state.abb) #Removes territories and Canada
  
```
`
# Export left-out names for US News search
```{r}
#write.csv(names_leftout, file = "NoDoximity_191015.csv")
```

# Combine data and remove duplicates
```{r}
dat <- full_join(additional, additional_DO) %>%
  full_join(additional_US) %>%
  arrange(., desc(address.info)) %>%
  group_by(Name) %>%
  filter(row_number() == 1)
  
```

# Calculate year of certification
```{r}
dat <- left_join(dat, abom)
dat$Date <- as.Date(dat$Initial.Certification, "%m/%d/%Y")
dat$Year <- substring(dat$Date, 1, 4) #Some are listed well before ABOM -- Maybe they listed birthdate? 
# Consider pulling final certification date and subtracting ten to get actual certification
```

# Remove all Canada State/Province Affiliation
```{r}
canada <- filter(dat, State.Province == "NL" | State.Province == "PE" | State.Province == "NS" | State.Province == "NB" | State.Province == "QC" | State.Province == "ON" | State.Province == "MB" | State.Province == "SK" | State.Province == "AB" | State.Province == "BC" | State.Province == "YT" | State.Province == "NT" | State.Province == "NU")

dat %<>%
  filter(!(State.Province %in% canada$State.Province))
```

# Extract Addresses
```{r}
 dat <- separate(dat, col = "address.info",into = c("Drop", "Address"), sep = c("Office Address"))
 dat <- separate(dat, col = "Address", into = c("Address", "Phone"), sep = c("Phone"))
 dat <- separate(dat, col = "Address", into = c("Address", "Drop"), sep = c("Is this information wrong?"))
 dat <- dat %>%
   select(-c(Phone, Drop))
```

# Hospital Affiliations
```{r}
dat <- separate(dat, col = "hospital.info", into = c("Drop", "Hospital"), sep = c("Hospital Affiliations")) %>% select(-c(Drop)) #Separate out hospital information

new_hospitals <- dat %>%
  select(Name, Hospital, Year) #Create a new list with variables of interest

new_hospitals <- na.omit(new_hospitals) #Removes rows without a hospital
new_hospitals$Hospital <- as.character(new_hospitals$Hospital) #Turns variable into a character

hospitals$states <- abbr2state(hospitals$STATE_ALPHA)
names <- lapply(new_hospitals$Hospital, function(x) {
  test <- tstrsplit(gsub('([[:upper:]])', ' \\1', x), ", ") #Split on the upper case letter and add a space
  if (length(test) > 1) { #If multiple hospitals 
    for (i in 2:(length(test))) { # For each one
      if (strsplit(test[[i]], " ")[[1]][2] %in% c("New", "North", "South", "West", "Rhode")) { #For states with two-word names
        state <- paste(strsplit(test[[i]], " ")[[1]][2], strsplit(test[[i]], " ")[[1]][4]) #Capture the state variable
        test[[i-1]] <- paste(test[[i-1]], state) #For the row, keep the state
        test[[i]] <- paste(strsplit(test[[i]], " ")[[1]][5:length(strsplit(test[[i]], " ")[[1]])], collapse = " ") #Keep the hospital name
        
      } else if (strsplit(test[[i]], " ")[[1]][2] %in% unique(hospitals$states)) { #If statename is unique
        test[[i-1]] <- paste(test[[i-1]], strsplit(test[[i]], " ")[[1]][2]) #Capture the state name
        test[[i]] <- paste(strsplit(test[[i]], " ")[[1]][3:length(strsplit(test[[i]], " ")[[1]])], collapse = " ") #Capture the hospital name
      }
    }
    test <- test[1:(length(test)-1)] #Save the test name for all
  }
})

holder <- as.data.frame(cbind(new_hospitals$Name, names)) #Attaches the list of names to the corresponding hospital
unlist_names <- unlist(holder$names) #Extends out the list of names

length_names <- lapply(1:nrow(holder), function(x) {
  length(holder$names[x][[1]])}) #For each row, calculate the number of hospitals associated with each individual
length_names <- unlist(length_names) #Extend out the number of hospitals affiliated with each name

diplomates <- unlist(holder$V1) #Unlist the names of the diplomates

final_diplomates <- as.data.frame(cbind(rep(diplomates, length_names), unlist_names)) #Creates final data set of diplomates and their corresponding institutions, correctly spelled without any odd spellings

colnames(final_diplomates) <- c("Name", "Hospital") #Renames columns
final_diplomates$Hospital <- as.character(final_diplomates$Hospital) #Change hospital column into a character

# If the last word is not a state, combine it with the next row and delete the next row. -- Remember to do this for both diplomates_states and final_diplomates

i = 1 #Initialize counter
while (i < nrow(final_diplomates)) { #While the counter is not equal to the length of the database 
  split <- strsplit(final_diplomates[i,2], " ") #Split on the space for the hospital of interest
  if (!(tail(split[[1]], n = 1) %in% hospitals$states)) { #If last word is not a state
    if (!(paste(tail(split[[1]], n = 2), collapse = " ") %in% hospitals$states)) { #If combinations of last two words is not a state
    final_diplomates[i, 2] <- paste(final_diplomates[i,2], final_diplomates[i+1,2]) #Combine the ith and ith + 1 hospital names
    final_diplomates <- final_diplomates[-(i+1),] #Remove problematic row
    }
  }
  i = i + 1
}

diplomates_states <- final_diplomates # Remake diplomate data set with same number of diplomates

diplomates_states$Hospital <- lapply(diplomates_states$Hospital, function(x){ #For each hospital
  split <- strsplit(x, " ") #Split on the space
  #If the last two words are "West Virginia", save as West Virginia, else check 
  ifelse(paste(tail(split[[1]], n = 2), collapse = " ") == "West Virginia", "West Virginia",
         ifelse(tail(split[[1]], n = 1) %in% hospitals$states, tail(split[[1]], n = 1), paste(tail(split[[1]], n = 2), collapse = " ")))
  #Keep only the state
})

diplomates_states$Hospital <- unlist(diplomates_states$Hospital)
diplomates_states <- filter(diplomates_states, Name != "Maribel Campos") #Removing Puerto Rico
final_diplomates <- filter(final_diplomates, Name != "Maribel Campos") #Removing Puerto Rico

final_diplomates$Hospital <- as.character(final_diplomates$Hospital) #Converts hospital to character

final_diplomates$Hospital <- ifelse(startsWith(final_diplomates$Hospital, " "), sub(".", "", final_diplomates$Hospital), final_diplomates$Hospital) #Removes words that start with a space with nothing

final_diplomates <- final_diplomates %>%
  group_by(Hospital) %>% #Group by hospital
  mutate("Final_Count" = sum(n())) #Count the amount of diplomates at each hospital 

```

# Geocode hospital locations -- CHECKED
```{r}
library(ggmap)
register_google("REMOVED") #API Key
final_diplomates$coordinates <- lapply(final_diplomates$Hospital, geocod2e) #Geocode hospital locations

final_diplomates %<>% 
  unnest(coordinates) #Unnest coordinates into two columns
#setwd("/Users/cpollack/Documents/GitHub/ObesityCertification/Scripts")
#write.csv(final_diplomates, "201104_HospitalsWithLocations.csv") #Save -- 2138 of the 2145 able to be successfully geocoded
```

# Figure out which people don't have hospitals that were geocoded -- CHECKED
```{r}
address_no_hospital <- filter(dat, is.na(Hospital) & address.info != "") #702 where address is not missing but hospital is
#setwd("/Users/cpollack/Documents/GitHub/ObesityCertification/Scripts")
#write.csv(address_no_hospital, "201104_HospitalsAddressOnly_NoGeocode.csv") #Save

address_no_hospital$coordinates <- lapply(address_no_hospital$address.info, geocode) #Geocode hospital locations

address_no_hospital %<>%
  unnest(coordinates)

#write.csv(address_no_hospital, "201104_HospitalsWithLocations_Addresses.csv") #Save
#address_no_hospital <- read.csv("201104_HospitalsWithLocations_Addresses.csv")
```

# Prep data set that was originally missed and geocode -- CHECKED
```{r}
originally_missed_hospitals <- as.data.frame(unlist(strsplit(originally_missed$Hospital.Affiliations, ";")), stringsAsFactors = FALSE) #Pull out all the hospitals
colnames(originally_missed_hospitals) <- "Hospitals" #839 #Rename column
originally_missed_hospitals %<>% 
  filter(Hospitals != " ") #%>% #823 #Keep only those that are labeled
  unique(.) #807 #Keep one row per hospital
#write.csv(originally_missed_hospitals, "201104_OriginallyMissedHospitals_NoGeocode.csv") #Save

originally_missed_address <- filter(originally_missed, Hospital.Affiliations == "" & Office.Address != "") #38
#write.csv(originally_missed_address, "201104_OriginallyMissedAddresses_NoGeocode.csv") #Save

originally_missed_hospitals$coordinates <- lapply(originally_missed_hospitals$Hospitals, geocode) #Geocode hospital locations
originally_missed_hospitals %<>% 
  unnest(coordinates) #Unnest coordinates into two columns
#write.csv(originally_missed_hospitals, "201104_OriginallyMissedHospitals.csv") #Save
originally_missed_hospitals <- read.csv("201104_OriginallyMissedHospitals.csv") #Save

originally_missed_address$coordinates <- lapply(originally_missed_address$Office.Address, geocode) #Geocode hospital locations
originally_missed_address %<>% 
  unnest(coordinates) #Unnest coordinates into two columns
#write.csv(originally_missed_address, "201104_OriginallyMissedAddresses.csv") #Save
originally_missed_address <- read.csv("200505_OriginallyMissedAddresses.csv")
```

# Extract data sets by year 
```{r}
years <- dat %>%
  select(Name, Year)

final_diplomates %<>% 
  select(Name, Hospital)

final_diplomates$Hospital <- ifelse(startsWith(final_diplomates$Hospital, " "), sub(".", "", final_diplomates$Hospital), final_diplomates$Hospital)

#Spot-check 35 that are missing and update
hospitals_to_correct$lon[48] <- -149.828537
hospitals_to_correct$lat[48] <- 61.211060
hospitals_to_correct$lon[53] <- -72.263743
hospitals_to_correct$lat[53] <- 43.640757
hospitals_to_correct$lon[103] <- -96.713714
hospitals_to_correct$lat[103] <- 43.534672
hospitals_to_correct$lon[155] <- -97.364119
hospitals_to_correct$lat[155] <- -97.364119
hospitals_to_correct$lon[164] <- -83.214608
hospitals_to_correct$lat[164] <- 42.291026
hospitals_to_correct$lon[170] <- -81.192609
hospitals_to_correct$lat[170] <- 37.765706
hospitals_to_correct$lon[317] <- -84.501077
hospitals_to_correct$lat[317] <- 39.140834
hospitals_to_correct$lon[321] <- -96.704866
hospitals_to_correct$lat[321] <- 32.834528
hospitals_to_correct$lon[401] <- -89.465406
hospitals_to_correct$lat[401] <- 43.567121
hospitals_to_correct$lon[582] <- NA #Unsure
hospitals_to_correct$lat[582] <- NA #Unsure
hospitals_to_correct$lon[591] <- -87.699570
hospitals_to_correct$lat[591] <- 34.746289
hospitals_to_correct$lon[662] <- -77.226588
hospitals_to_correct$lat[662] <- 38.856687
hospitals_to_correct$lon[732] <- -122.058465
hospitals_to_correct$lat[732] <- 37.892533
hospitals_to_correct$lon[1075] <- -71.246518
hospitals_to_correct$lat[1075] <- 42.330905
hospitals_to_correct$lon[1120] <- -88.343778
hospitals_to_correct$lat[1120] <- 41.887455
hospitals_to_correct$lon[1130] <- -80.823066
hospitals_to_correct$lat[1130] <- 35.210634
hospitals_to_correct$lon[1203] <- -71.316645
hospitals_to_correct$lat[1203] <- 42.877065
hospitals_to_correct$lon[1233] <- -84.984217
hospitals_to_correct$lat[1233] <- 32.480588
hospitals_to_correct$lon[1269] <- -122.204749
hospitals_to_correct$lat[1269] <- 48.000165
hospitals_to_correct$lon[1281] <- -122.295565
hospitals_to_correct$lat[1281] <- 38.325175
hospitals_to_correct$lon[1309] <- -117.380598
hospitals_to_correct$lat[1309] <- 33.976763
hospitals_to_correct$lon[1310] <- -76.482420
hospitals_to_correct$lat[1310] <- 37.064123
hospitals_to_correct$lon[1327] <- -88.270755
hospitals_to_correct$lat[1327] <- 41.729298
hospitals_to_correct$lon[1369] <- -117.833561
hospitals_to_correct$lat[1369] <- 34.097840
hospitals_to_correct$lon[1380] <- -82.531299
hospitals_to_correct$lat[1380] <- 27.31883
hospitals_to_correct$lon[1428] <- -73.629955
hospitals_to_correct$lat[1428] <- 40.652189
hospitals_to_correct$lon[1440] <- -73.207108
hospitals_to_correct$lat[1440] <- 42.874636
hospitals_to_correct$lon[1473] <- -94.168733
hospitals_to_correct$lat[1473] <- 45.574530
hospitals_to_correct$lon[1477] <- -90.164736
hospitals_to_correct$lat[1477] <- 32.332857
hospitals_to_correct$lon[1486] <- -84.959309
hospitals_to_correct$lat[1486] <- 32.505536
hospitals_to_correct$lon[1496] <- -89.645506
hospitals_to_correct$lat[1496] <- 39.804868
hospitals_to_correct$lon[1526] <- -90.500936
hospitals_to_correct$lat[1526] <- 38.653003
hospitals_to_correct$lon[1559] <- -90.500936
hospitals_to_correct$lat[1559] <- 30.108631
hospitals_to_correct$lon[1562] <- -73.201481
hospitals_to_correct$lat[1562] <- 41.201669
hospitals_to_correct$lon[1588] <- -121.249216
hospitals_to_correct$lat[1588] <- 38.765895

dip_year_hospital <- inner_join(years, final_diplomates, by = "Name") %>%
  full_join(., hospitals_to_correct, by = "Hospital") %>%
  filter(is.na(Hospital) == FALSE)

#4,150 instances
dip_11_hop <- filter(dip_year_hospital, Year == 2011) %>%
  distinct(Hospital, .keep_all = TRUE) #38 diplomates, 60 unique hospitals
dip_12_hop <- filter(dip_year_hospital, Year <= 2012)  %>%
  distinct(Hospital, .keep_all = TRUE) #347 diplomates, 523 hospitals
dip_13_hop <- filter(dip_year_hospital, Year <= 2013) %>%
  distinct(Hospital, .keep_all = TRUE) #487 diplomates, 691 hospitals
dip_14_hop <- filter(dip_year_hospital, Year <= 2014) %>%
  distinct(Hospital, .keep_all = TRUE) #497 diplomates, 702 hospitals
dip_15_hop <- filter(dip_year_hospital, Year <= 2015) %>%
  distinct(Hospital, .keep_all = TRUE) #773 diplomates, 952 hospitals
dip_16_hop <- filter(dip_year_hospital, Year <= 2016) %>%
  distinct(Hospital, .keep_all = TRUE) #1011 diplomates, 1176 hospitals
dip_17_hop <- filter(dip_year_hospital, Year <= 2017) %>%
  distinct(Hospital, .keep_all = TRUE) #1321 diplomates, 1439 hospitals
dip_18_hop <- filter(dip_year_hospital, Year <= 2018) %>%
  distinct(Hospital, .keep_all = TRUE) #1692 diplomates, 1667 hospitals
dip_19_hop <- filter(dip_year_hospital, Year <= 2019) %>%
  distinct(Hospital, .keep_all = TRUE) #2145 diplomates, 1872 hospitals
```

# Repeat above, but with address file.
```{r}
address_no_hospital %<>%
  select(Name, address.info, Year, lon, lat)

address_no_hospital$lon[16] <- -70.386375
address_no_hospital$lat[16] <- 43.458468
address_no_hospital$lon[38] <- -122.477028
address_no_hospital$lat[38] <- 47.242326
address_no_hospital$lon[94] <- -76.817576
address_no_hospital$lat[94] <- 40.283692
address_no_hospital$lon[140] <- -76.139179
address_no_hospital$lat[140] <- 43.042478
address_no_hospital$lon[141] <- -155.981035
address_no_hospital$lat[141] <- 19.626998
address_no_hospital$lon[146] <- -105.078624
address_no_hospital$lat[146] <- 39.880786
address_no_hospital$lon[180] <- -86.048004
address_no_hospital$lat[180] <- 39.905668
address_no_hospital$lon[241] <- -115.297423
address_no_hospital$lat[241] <- 36.090438
address_no_hospital$lon[258] <- -121.310344
address_no_hospital$lat[258] <- 38.761031
address_no_hospital$lon[283] <- -111.983103
address_no_hospital$lat[283] <- 33.641667
address_no_hospital$lon[298] <- -118.262254
address_no_hospital$lat[298] <- 34.158859
address_no_hospital$lon[309] <- -97.876211
address_no_hospital$lat[309] <- 30.029331
address_no_hospital$lon[440] <- -82.834997
address_no_hospital$lat[440] <- 27.937137
address_no_hospital$lon[470] <- -80.259070
address_no_hospital$lat[470] <- 26.118161
address_no_hospital$lon[554] <- -81.786235
address_no_hospital$lat[554] <- 26.213120
address_no_hospital$lon[588] <- -71.069131
address_no_hospital$lat[588] <- 42.344073

address_no_hospital <- address_no_hospital[-68,] #Remove PR

#711 instances
dip_11_add <- filter(address_no_hospital, Year <= 2011) %>%
  distinct(address.info, .keep_all = TRUE) #78 diplomates, 78 unique hospitals
dip_12_add <- filter(address_no_hospital, Year <= 2012)  %>%
  distinct(address.info, .keep_all = TRUE) #132 diplomates, 132 hospitals
dip_13_add <- filter(address_no_hospital, Year <= 2013) %>%
  distinct(address.info, .keep_all = TRUE) #184 diplomates, 184 hospitals
dip_14_add <- filter(address_no_hospital, Year <= 2014) %>%
  distinct(address.info, .keep_all = TRUE) #192 diplomates, 192 hospitals
dip_15_add <- filter(address_no_hospital, Year <= 2015) %>%
  distinct(address.info, .keep_all = TRUE) #256 diplomates, 256 hospitals
dip_16_add <- filter(address_no_hospital, Year <= 2016) %>%
  distinct(address.info, .keep_all = TRUE) #342 diplomates, 342 hospitals
dip_17_add <- filter(address_no_hospital, Year <= 2017) %>%
  distinct(address.info, .keep_all = TRUE) #445 diplomates, 445 hospitals
dip_18_add <- filter(address_no_hospital, Year <= 2018) %>%
  distinct(address.info, .keep_all = TRUE) #558 diplomates, 558 hospitals
dip_19_add <- filter(address_no_hospital, Year <= 2019) %>%
  distinct(address.info, .keep_all = TRUE) #711 diplomates, 711 hospitals

```

# Repeat the above, but with the originally missed hospital file
```{r}
years <- dat %>%
  select(Name, Year)

which(is.na(originally_missed_hospitals$lon))

#Spot-check 35 that are missing and update
originally_missed_hospitals$lon[6] <- -87.513936
originally_missed_hospitals$lat[6] <- 33.198222
originally_missed_hospitals$lon[349] <- -83.051795
originally_missed_hospitals$lat[349] <- 42.353540
originally_missed_hospitals$lon[363] <- -83.682160
originally_missed_hospitals$lat[363] <- 42.317731
originally_missed_hospitals$lon[405] <- -80.854599
originally_missed_hospitals$lat[405] <- 35.057202
originally_missed_hospitals$lon[611] <- -75.517324
originally_missed_hospitals$lat[611] <- 40.567154
originally_missed_hospitals$lon[718] <- -96.345225
originally_missed_hospitals$lat[718] <- 30.657871
originally_missed_hospitals$lon[761] <- -73.200890
originally_missed_hospitals$lat[761] <- 44.480255

originally_missed_hospitals_names <- originally_missed %>% #Original file
  select(Name, Year, Hospital.Affiliations) %>% #Pull out only relevant variables
  filter(Hospital.Affiliations != " " & Hospital.Affiliations != "") %>% #Remove unlisted hospitals
  separate_rows(Hospital.Affiliations, sep = ";") %>% #Separate out the rows by semi-colon
  filter(Hospital.Affiliations != " " & Hospital.Affiliations != "") %>% #Remove those that had an extra space
  left_join(., originally_missed_hospitals, by = c("Hospital.Affiliations" = "Hospitals")) #Left join person file with hospital lat-lon file

#823 instances
dip_11_hop_missed <- filter(originally_missed_hospitals_names, Year == 2011) %>%
  distinct(Hospital.Affiliations, .keep_all = TRUE) #3 diplomates, 3 unique hospitals
dip_12_hop_missed <- filter(originally_missed_hospitals_names, Year <= 2012)  %>%
  distinct(Hospital.Affiliations, .keep_all = TRUE) #147 diplomates, 147 hospitals
dip_13_hop_missed <- filter(originally_missed_hospitals_names, Year <= 2013) %>%
  distinct(Hospital.Affiliations, .keep_all = TRUE) #209 diplomates, 209 hospitals
dip_14_hop_missed <- filter(originally_missed_hospitals_names, Year <= 2014) %>%
  distinct(Hospital.Affiliations, .keep_all = TRUE) #213 diplomates, 212 hospitals
dip_15_hop_missed <- filter(originally_missed_hospitals_names, Year <= 2015) %>%
  distinct(Hospital.Affiliations, .keep_all = TRUE) #290 diplomates, 289 hospitals
dip_16_hop_missed <- filter(originally_missed_hospitals_names, Year <= 2016) %>%
  distinct(Hospital.Affiliations, .keep_all = TRUE) #408 diplomates, 407 hospitals
dip_17_hop_missed <- filter(originally_missed_hospitals_names, Year <= 2017) %>%
  distinct(Hospital.Affiliations, .keep_all = TRUE) #518 diplomates, 513 hospitals
dip_18_hop_missed <- filter(originally_missed_hospitals_names, Year <= 2018) %>%
  distinct(Hospital.Affiliations, .keep_all = TRUE) #678 diplomates, 669 hospitals
dip_19_hop_missed <- filter(originally_missed_hospitals_names, Year <= 2019) %>%
  distinct(Hospital.Affiliations, .keep_all = TRUE) #823 diplomates, 807 hospitals

```

# Repeat above, but with addresses 
```{r}
which(is.na(originally_missed_address$lon))

originally_missed_address$lon[8] <- -121.456301
originally_missed_address$lat[8] <- 38.556296
originally_missed_address$lon[12] <- -105.131378
originally_missed_address$lat[12] <- 39.718870

originally_missed_address %<>%
  select(Name, Year, Office.Address, lon, lat)

#38 instances
dip_11_add_missed <- filter(originally_missed_address, Year == 2011) %>%
  distinct(Office.Address, .keep_all = TRUE) #0 diplomates, 0 unique hospitals
dip_12_add_missed <- filter(originally_missed_address, Year <= 2012)  %>%
  distinct(Office.Address, .keep_all = TRUE) #6 diplomates, 6 hospitals
dip_13_add_missed <- filter(originally_missed_address, Year <= 2013) %>%
  distinct(Office.Address, .keep_all = TRUE) #7 diplomates, 7 hospitals
dip_14_add_missed <- filter(originally_missed_address, Year <= 2014) %>%
  distinct(Office.Address, .keep_all = TRUE) #7 diplomates, 7 hospitals
dip_15_add_missed <- filter(originally_missed_address, Year <= 2015) %>%
  distinct(Office.Address, .keep_all = TRUE) #14 diplomates, 14 hospitals
dip_16_add_missed <- filter(originally_missed_address, Year <= 2016) %>%
  distinct(Office.Address, .keep_all = TRUE) #17 diplomates, 17 hospitals
dip_17_add_missed <- filter(originally_missed_address, Year <= 2017) %>%
  distinct(Office.Address, .keep_all = TRUE) #22 diplomates, 22 hospitals
dip_18_add_missed <- filter(originally_missed_address, Year <= 2018) %>%
  distinct(Office.Address, .keep_all = TRUE) #38 diplomates, 38 hospitals
dip_19_add_missed <- filter(originally_missed_address, Year <= 2019) %>%
  distinct(Office.Address, .keep_all = TRUE) #38 diplomates, 38 hospitals

```

# Combine hospital and address
```{r}
address_no_hospital$lonlat <- paste(address_no_hospital$lon, ",", address_no_hospital$lat)
hospitals_to_correct$lonlat <- paste(hospitals_to_correct$lon, ",", hospitals_to_correct$lat)

originally_missed_hospitals_names %<>%
  select(-X)

colnames(originally_missed_hospitals_names)[3] <- "Hospital"
colnames(originally_missed_address)[3] <- "Hospital"

originally_missed_hospitals_names$latlon <- paste(originally_missed_hospitals_names$lat, ",", originally_missed_hospitals_names$lon)
originally_missed_address$latlon <- paste(originally_missed_address$lat, ",", originally_missed_address$lon)

dat_diplomates <- as.data.frame(rbind(dat_diplomates, as.data.frame(originally_missed_hospitals_names), as.data.frame(originally_missed_address)))

length(unique(dat_diplomates$Name)) #3,227

dip_11_all <- filter(dat_diplomates, Year <= 2011) %>%
  distinct(latlon, .keep_all = TRUE)
dip_12_all <- filter(dat_diplomates, Year <= 2012) %>%
  distinct(latlon, .keep_all = TRUE)
dip_13_all <- filter(dat_diplomates, Year <= 2013) %>%
  distinct(latlon, .keep_all = TRUE)
dip_14_all <- filter(dat_diplomates, Year <= 2014) %>%
  distinct(latlon, .keep_all = TRUE)
dip_15_all <- filter(dat_diplomates, Year <= 2015) %>%
  distinct(latlon, .keep_all = TRUE)
dip_16_all <- filter(dat_diplomates, Year <= 2016) %>%
  distinct(latlon, .keep_all = TRUE)
dip_17_all <- filter(dat_diplomates, Year <= 2017) %>%
  distinct(latlon, .keep_all = TRUE)
dip_18_all <- filter(dat_diplomates, Year <= 2018) %>%
  distinct(latlon, .keep_all = TRUE)
dip_19_all <- filter(dat_diplomates, Year <= 2019) %>%
  distinct(latlon, .keep_all = TRUE)
```

# Save all files
```{r}
#setwd("~/Documents/Dartmouth/Research/Obesity Certification/Data")
#write.csv(dip_11_all, "200505_Hospitals_2011.csv")
#write.csv(dip_12_all, "200505_Hospitals_2012.csv")
#write.csv(dip_13_all, "200505_Hospitals_2013.csv")
#write.csv(dip_14_all, "200505_Hospitals_2014.csv")
#write.csv(dip_15_all, "200505_Hospitals_2015.csv")
#write.csv(dip_16_all, "200505_Hospitals_2016.csv")
#write.csv(dip_17_all, "200505_Hospitals_2017.csv")
#write.csv(dip_18_all, "200505_Hospitals_2018.csv")
#write.csv(dip_19_all, "200505_Hospitals_2019.csv")
```

# Extract all missing values
```{r}
#missing <- filter(dat, is.na(Address) & is.na(Hospital))
#write.csv(missing[,c(1, 20:25)], "missing_data.csv")
```

# Take out individuals with "Canada" listed in ABOM
```{r}
dat_diplomates_no_canada <- dat_diplomates[-which(dat_diplomates$Name %in% canada$Name),]

dip_11_all_nc <- filter(dat_diplomates_no_canada, Year <= 2011) %>%
  distinct(latlon, .keep_all = TRUE)
dip_12_all_nc <- filter(dat_diplomates_no_canada, Year <= 2012) %>%
  distinct(latlon, .keep_all = TRUE)
dip_13_all_nc <- filter(dat_diplomates_no_canada, Year <= 2013) %>%
  distinct(latlon, .keep_all = TRUE)
dip_14_all_nc <- filter(dat_diplomates_no_canada, Year <= 2014) %>%
  distinct(latlon, .keep_all = TRUE)
dip_15_all_nc <- filter(dat_diplomates_no_canada, Year <= 2015) %>%
  distinct(latlon, .keep_all = TRUE)
dip_16_all_nc <- filter(dat_diplomates_no_canada, Year <= 2016) %>%
  distinct(latlon, .keep_all = TRUE)
dip_17_all_nc <- filter(dat_diplomates_no_canada, Year <= 2017) %>%
  distinct(latlon, .keep_all = TRUE)
dip_18_all_nc <- filter(dat_diplomates_no_canada, Year <= 2018) %>%
  distinct(latlon, .keep_all = TRUE)
dip_19_all_nc <- filter(dat_diplomates_no_canada, Year <= 2019) %>%
  distinct(latlon, .keep_all = TRUE)

#setwd("~/Documents/Dartmouth/Research/Obesity Certification/Data")
#write.csv(dip_11_all_nc, "200505_Hospitals_2011_NC.csv")
#write.csv(dip_12_all_nc, "200505_Hospitals_2012_NC.csv")
#write.csv(dip_13_all_nc, "200505_Hospitals_2013_NC.csv")
#write.csv(dip_14_all_nc, "200505_Hospitals_2014_NC.csv")
#write.csv(dip_15_all_nc, "200505_Hospitals_2015_NC.csv")
#write.csv(dip_16_all_nc, "200505_Hospitals_2016_NC.csv")
#write.csv(dip_17_all_nc, "200505_Hospitals_2017_NC.csv")
#write.csv(dip_18_all_nc, "200505_Hospitals_2018_NC.csv")
#write.csv(dip_19_all_nc, "200505_Hospitals_2019_NC.csv")

```

#  Separate pediatric and adult
```{r}
pediatric_only <- dat[grep("Pediatrics", dat$Additional.Board.Certification),]
adult_only <- anti_join(dat, pediatric_only)
pediatrics_internal_med <- pediatric_only[grep("Internal Medicine", pediatric_only$Additional.Board.Certification),]
family_medicine <- adult_only[grep("Family Medicine", adult_only$Additional.Board.Certification),]

adult_only <- rbind(adult_only, pediatrics_internal_med)
adult_only %<>%
  filter(Additional.Board.Certification != "")
pediatric_only <- rbind(pediatric_only, family_medicine)

missing_certification <- dat %>% filter(Additional.Board.Certification == "")
setwd("~/Documents/Dartmouth/Research/Obesity Certification/Data")
#write.csv(missing_certification, "201008_MissingCertification.csv")
missing_certification_complete <- read.csv("201008_MissingCertification.csv")

missing_certification_pediatric_only <- missing_certification_complete[grep("Pediatrics", missing_certification_complete$Additional.Board.Certification),]

missing_certification_complete_adult_only <- anti_join(missing_certification_complete, missing_certification_pediatric_only)

missing_certification_pediatrics_internal_med <- missing_certification_pediatric_only[grep("Internal Medicine", missing_certification_pediatric_only$Additional.Board.Certification),]

missing_certification_family_medicine <- missing_certification_complete_adult_only[grep("Family Medicine", missing_certification_complete_adult_only$Additional.Board.Certification),]

missing_certification_adult_only <- rbind(missing_certification_complete_adult_only, missing_certification_pediatrics_internal_med) # 108
missing_certification_adult_only %<>%
  filter(Additional.Board.Certification != "")

missing_certification_pediatric_only <- rbind(missing_certification_pediatric_only, missing_certification_family_medicine) # 59

dat_diplomate_adult <- rbind(adult_only, )


adult_dip_11_all_nc <- filter(dat_diplomates_no_canada, Year <= 2011 & 
                                (Name %in% adult_only$Name | Name %in% missing_certification_adult_only$Name)) %>%
  distinct(latlon, .keep_all = TRUE)
adult_dip_12_all_nc <- filter(dat_diplomates_no_canada, Year <= 2012 & 
                                (Name %in% adult_only$Name | Name %in% missing_certification_adult_only$Name)) %>%
  distinct(latlon, .keep_all = TRUE)
adult_dip_13_all_nc <- filter(dat_diplomates_no_canada, Year <= 2013 & 
                                (Name %in% adult_only$Name | Name %in% missing_certification_adult_only$Name)) %>%
  distinct(latlon, .keep_all = TRUE)
adult_dip_14_all_nc <- filter(dat_diplomates_no_canada, Year <= 2014 & 
                                (Name %in% adult_only$Name | Name %in% missing_certification_adult_only$Name)) %>%
  distinct(latlon, .keep_all = TRUE)
adult_dip_15_all_nc <- filter(dat_diplomates_no_canada, Year <= 2015 & 
                                (Name %in% adult_only$Name | Name %in% missing_certification_adult_only$Name)) %>%
  distinct(latlon, .keep_all = TRUE)
adult_dip_16_all_nc <- filter(dat_diplomates_no_canada, Year <= 2016 & 
                                (Name %in% adult_only$Name | Name %in% missing_certification_adult_only$Name)) %>%
  distinct(latlon, .keep_all = TRUE)
adult_dip_17_all_nc <- filter(dat_diplomates_no_canada, Year <= 2017 & 
                                (Name %in% adult_only$Name | Name %in% missing_certification_adult_only$Name)) %>%
  distinct(latlon, .keep_all = TRUE)
adult_dip_18_all_nc <- filter(dat_diplomates_no_canada, Year <= 2018 & 
                                (Name %in% adult_only$Name | Name %in% missing_certification_adult_only$Name)) %>%
  distinct(latlon, .keep_all = TRUE)
adult_dip_19_all_nc <- filter(dat_diplomates_no_canada, Year <= 2019 & 
                                (Name %in% adult_only$Name | Name %in% missing_certification_adult_only$Name)) %>%
  distinct(latlon, .keep_all = TRUE)

pediatric_dip_11_all_nc <- filter(dat_diplomates_no_canada, Year <= 2011 & 
                                (Name %in% pediatric_only$Name | Name %in% missing_certification_pediatric_only$Name)) %>%
  distinct(latlon, .keep_all = TRUE)
pediatric_dip_12_all_nc <- filter(dat_diplomates_no_canada, Year <= 2012 & 
                                (Name %in% pediatric_only$Name | Name %in% missing_certification_pediatric_only$Name)) %>%
  distinct(latlon, .keep_all = TRUE)
pediatric_dip_13_all_nc <- filter(dat_diplomates_no_canada, Year <= 2013 & 
                                (Name %in% pediatric_only$Name | Name %in% missing_certification_pediatric_only$Name)) %>%
  distinct(latlon, .keep_all = TRUE)
pediatric_dip_14_all_nc <- filter(dat_diplomates_no_canada, Year <= 2014 & 
                                (Name %in% pediatric_only$Name | Name %in% missing_certification_pediatric_only$Name)) %>%
  distinct(latlon, .keep_all = TRUE)
pediatric_dip_15_all_nc <- filter(dat_diplomates_no_canada, Year <= 2015 & 
                                (Name %in% pediatric_only$Name | Name %in% missing_certification_pediatric_only$Name)) %>%
  distinct(latlon, .keep_all = TRUE)
pediatric_dip_16_all_nc <- filter(dat_diplomates_no_canada, Year <= 2016 & 
                                (Name %in% pediatric_only$Name | Name %in% missing_certification_pediatric_only$Name)) %>%
  distinct(latlon, .keep_all = TRUE)
pediatric_dip_17_all_nc <- filter(dat_diplomates_no_canada, Year <= 2017 & 
                                (Name %in% pediatric_only$Name | Name %in% missing_certification_pediatric_only$Name)) %>%
  distinct(latlon, .keep_all = TRUE)
pediatric_dip_18_all_nc <- filter(dat_diplomates_no_canada, Year <= 2018 & 
                                (Name %in% pediatric_only$Name | Name %in% missing_certification_pediatric_only$Name)) %>%
  distinct(latlon, .keep_all = TRUE)
pediatric_dip_19_all_nc <- filter(dat_diplomates_no_canada, Year <= 2019 & 
                                (Name %in% pediatric_only$Name | Name %in% missing_certification_pediatric_only$Name)) %>%
  distinct(latlon, .keep_all = TRUE)

setwd("~/Documents/Dartmouth/Research/Obesity Certification/Data")
#write.csv(adult_dip_11_all_nc, "201009_Hospitals_2011_NC_Adult.csv")
#write.csv(adult_dip_12_all_nc, "201009_Hospitals_2012_NC_Adult.csv")
#write.csv(adult_dip_13_all_nc, "201009_Hospitals_2013_NC_Adult.csv")
#write.csv(adult_dip_14_all_nc, "201009_Hospitals_2014_NC_Adult.csv")
#write.csv(adult_dip_15_all_nc, "201009_Hospitals_2015_NC_Adult.csv")
#write.csv(adult_dip_16_all_nc, "201009_Hospitals_2016_NC_Adult.csv")
##write.csv(adult_dip_17_all_nc, "201009_Hospitals_2017_NC_Adult.csv")
#write.csv(adult_dip_18_all_nc, "201009_Hospitals_2018_NC_Adult.csv")
#write.csv(adult_dip_19_all_nc, "201009_Hospitals_2019_NC_Adult.csv")

setwd("~/Documents/Dartmouth/Research/Obesity Certification/Data")
#write.csv(pediatric_dip_11_all_nc, "201009_Hospitals_2011_NC_Peds.csv")
#write.csv(pediatric_dip_12_all_nc, "201009_Hospitals_2012_NC_Peds.csv")
#write.csv(pediatric_dip_13_all_nc, "201009_Hospitals_2013_NC_Peds.csv")
#write.csv(pediatric_dip_14_all_nc, "201009_Hospitals_2014_NC_Peds.csv")
#write.csv(pediatric_dip_15_all_nc, "201009_Hospitals_2015_NC_Peds.csv")
#write.csv(pediatric_dip_16_all_nc, "201009_Hospitals_2016_NC_Peds.csv")
#write.csv(pediatric_dip_17_all_nc, "201009_Hospitals_2017_NC_Peds.csv")
#write.csv(pediatric_dip_18_all_nc, "201009_Hospitals_2018_NC_Peds.csv")
#write.csv(pediatric_dip_19_all_nc, "201009_Hospitals_2019_NC_Peds.csv")

```


